Subsegmental language detection in Celtic language text

### 2014-05-09 codeswitch-cltw-2014/codeswitch.tex
evaluation+
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@52658 72bbbca6-d526-0410-a7d9-f06f51895060

For our current task, each of the texts have been limited to two languages i.e. the primary and the secondary language. Hence the type of chunking tags are limited to these.

>>>>

For our current task, each of the texts have been limited to two languages i.e. the primary and the secondary language. Hence the type of chunking tags are limited to these. The evaluation statics shown in the Table mention two values for each of the experiment conducted on the three bilingual language datasets. The first, is the percentage of correctly detected phrases, which is the precision and the second is the number of phrases in the data that were found by the chunker, which is the recall.
